Do larger catchments respond different to forest cover change? Re-analysing a global data set.

### 2021-10-12 paper/Forest_and_Water/Forest_and_Water.Rmd
adding MODIS ET data large catchments

linear regression just looking at the change in forestry and the sign of the change (deforestation or forestation)

>>>>

We start of with a simple linear regression (i.e. following @zhang2017) just looking at the change in flow as a result in the percent change forestry and including the direction of the change, increase in forest cover, or decrease in forest cover.
